\documentclass[5p,sort&compress]{elsarticle}	
\newcommand{\RomanNumeralCaps}[1]
    {\MakeUppercase{\romannumeral #1}}
\makeatletter
\def\ps@pprintTitle{%
 \let\@oddhead\@empty
 \let\@evenhead\@empty
 \def\@oddfoot{\footnotesize\itshape
       \hfill\today}%
 \let\@evenfoot\@oddfoot}
\makeatother
\usepackage{dcolumn}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}

\usepackage{textcomp}
\usepackage{lmodern}
\renewenvironment{abstract}{\global\setbox\absbox=\vbox\bgroup
\hsize=\textwidth\def\baselinestretch{1}%
\noindent\unskip\textbf{Abstract}
\par\medskip\noindent\unskip\ignorespaces}
{\egroup}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{caption} %% figurer fugler
\usepackage{bm}
\usepackage{siunitx}
\sisetup{
exponent-product = \cdot,
output-decimal-marker  =  {.}, % komma-stil
separate-uncertainty = false, %true hvis du ikke vil ha usikkerhet i parentes
per-mode = symbol,
group-digits = false,
}
\usepackage{graphicx}
\renewcommand{\topfraction}{.85}
\renewcommand{\bottomfraction}{.7}
\renewcommand{\textfraction}{.15}
\renewcommand{\floatpagefraction}{.66}
\setcounter{topnumber}{3}
\setcounter{bottomnumber}{2}
\setcounter{totalnumber}{10}
\usepackage{flafter}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage[colorlinks,linkcolor=pink]{hyperref}
\hypersetup{
    colorlinks=true,
    linkcolor=purple,
    filecolor=magenta,      
    urlcolor=cyan,
    citecolor=purple
}
\usepackage{cleveref}
\usepackage{comment}
\usepackage{arydshln}
\usepackage[font=small,labelfont=bf]{caption}
\usepackage{subcaption}

% Dakrmode
\usepackage{xcolor}
% \pagecolor[rgb]{0.128, 0.128, 0.128}  %black
% \color[rgb]{0.848, 0.848, 0.848}  %grey

\urlstyle{same}



\begin{document}
\begin{frontmatter}

  % \title{TFE4575: Chemical methods for thin film deposition}
  % TODO: more exciting title
  %\title{Characterization of an Unknown Sample Using Scanning Electron Microscopy, Scanning Transmission Electron Microscopy, Energy Dispersive X-Ray Spectroscopy, Atomic Force Microscopy, and Raman Spectroscopy}
  \title{Sol-gel Fabrication and Characterization of a Barium Titanat Thin Film \\ \large{Thin film lab in TFE4575}}

  \author[fysikk]{Brynjar Morka Mæhlum}
  \author[fysikk]{Thord Niri Gjesdhal Heggren}


  \address[fysikk]{Department of Physics, Norwegian University of Science and Technology, 7491 Trondheim, Norway.}

  \begin{abstract}

    \noindent In this project, a barium titanat (BTO) thin film was made on a Si-Pt substrate using a sol-gel processing method.
    The BTO film was made by first making a barium sol, and then combining it with a premade titanium sol.
    This mixture was applied to the substrate using spin coating, followed by drying at 200°C and sintering at 700°C.
    The film was then characterized using an optical microscope, a stylus profilometer, and a scanning electron microscope.
    The thickness of the film was estimated to be 670 nm.
    The roughness was estimated to be 7.22 nm, measured as the STD of the surface profile from the profilometer.
    The optical microscope indicated that the film in general was homogenous, but that some artifacts were present.
    The SEM and profilometer gave more detailed information about the film morphology and the artifacts.
    Some artifacts were flaking, pinholes, film deformation and impurities.
    The profilometer gave very detailed and quantitative information about the measured lines, while the SEM gave more qualitative information with a fuller picture of the morphology.


  \end{abstract}


\end{frontmatter}

{ % Denne gjør table of contents pink i stedet for blå
\hypersetup{linkcolor=purple}
\tableofcontents
}

%%%%%%%%%%%%%%%%%%% THEORY %%%%%%%%%%%%%%%%%%
\section{Theory}

\input{chapters/theory.tex}

%%%%%%%%%%%%%%%%%%% METHODS %%%%%%%%%%%%%%%%%%
\section{Methods}
\input{chapters/methods.tex}



%%%%%%%%%%%%%%%%%%% RESULTS %%%%%%%%%%%%%%%%%%
\section{Results}
\input{chapters/results.tex}

%%%%%%%%%%%%%%%%%%% DISCUSSION %%%%%%%%%%%%%%%%%%
\section{Discussion}
\input{chapters/discussion.tex}

%%%%%%%%%%%%%%%%%%% CONCLUSION %%%%%%%%%%%%%%%%%%
\section{Conclusion}

\noindent In this project, a barium titanat thin film was made on a Si-Pt substrate using a sol-gel processing method.
The film was characterized using an optical microscope, a stylus profilometer, and a scanning electron microscope.
The characterization showed that the film was homogenous, but that some artifacts and defects were present.
Some artifacts were flaking, pinholes, film deformation and impurities.
The thickness of the film was measured to be 670 nm.
The profilometer gave a roughness of 7.22 nm, measured as the STD of the surface profile.
The SEM images gave the best morphology results, giving both a good overview and good insight into what might have caused the artifacts.


%%%%%%%%%%%%%% REFERANSER %%%%%%%%%%%%%%%%%%

\begingroup
\begin{center}
  \rule{2cm}{.4pt}
\end{center}
\makeatletter
\@beginparpenalty=10000
\makeatother
\bibliographystyle{unsrt} %unsrtnat
\bibliography{references}


\endgroup

\end{document}